WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-07-18 article/Article.tex
add itk.echo() doc
darcs-hash:20060718134932-2fc9d-e941acc055e353a984190aa5d7ed905a811e9485.gz

>>>>

  \item \verb$itk.echo(object, file)$ is a convenient function to call the \verb$Print()$
method of an ITK object without the need to pass a \verb$StringStream$ object.
This function is less useful with the optional patches: the \verb$__str__()$
method do a very similar job with a better integration with python.

Example:

\begin{verbatim}
12> itk.echo(median)
MedianImageFilter (0x82c5b68)
  RTTI typeinfo:   itk::MedianImageFilter<itk::Image<unsigned char, 3u>, itk::Image<unsigned char, 3u> >
  Reference Count: 1
  Modified Time: 10
  Debug: Off
  Observers:
    none
  Number Of Required Inputs: 1
  Number Of Required Outputs: 1
  Number Of Threads: 2
  ReleaseDataFlag: Off
  ReleaseDataBeforeUpdateFlag: Off
  No Inputs
  Output 0: (0x875da68)
  AbortGenerateData: Off
  Progress: 0
  Multithreader:
    RTTI typeinfo:   itk::MultiThreader
    Reference Count: 1
    Modified Time: 2
    Debug: Off
    Observers:
      none
    Thread Count: 2
    Global Maximum Number Of Threads: 0
  Radius: [1, 1, 1]
\end{verbatim}
